\chapter{References} 

\begin{enumerate}
\item Athavale, Y., Chavan, S., Gudadhe, S., & Jain, A. (2021). Real-time Sign Language
    Detection Using Machine Learning. \textit{International Journal of Innovative Technology
    and Exploring Engineering}, 10(5), 680-686.

    \item  Ghaderzadeh, M., Czyżewski, A., & Palus, H. (2021). Hand Gesture Recognition Using
Convolutional Neural Networks for Polish Sign Language. Sensors, 21(13), 4392.

    \item  Majumder, A., & Koushik, J. C. (2020). American Sign Language Detection Using
Deep Learning Techniques. In Proceedings of the 2nd International Conference on
Machine Learning and Soft Computing (pp. 167-175). Springer, Singapore.

    \item  Mohan, S., Pal, A., Roy, S., & Ramakrishnan, K. G. (2021). Sign Language Recognition
System Using Deep Learning. In 2021 IEEE International Conference on Power
Electronics, Smart Grid and Renewable Energy (PESGRE) (pp. 1-6). IEEE.

    \item  Perera, C. J., Jayasekara, P. P., & Rajapaksha, H. N. (2021). Sign Language Recognition
using Convolutional Neural Network. In 2021 Moratuwa Engineering Research
Conference (MERCon) (pp. 142-147). IEEE.

    \item  Cai, Y., Guan, H., Lin, C., & Zhao, X. (2021). Sign Language Recognition Using Deep
Learning Techniques: A Review. IEEE Access, 9, 33545-33557.

    \item  Huang, Y., Chen, Y., & You, X. (2020). Sign Language Recognition Based on MultiModal Deep Learning. IEEE Transactions on Multimedia, 22(10), 2700-2712.


    \item  Li, H., Huang, W., Zhang, X., & Lao, S. (2020). Deep Learning for Sign Language
Recognition and Translation: A Survey. IEEE Transactions on Human-Machine
Systems, 50(4), 295-307.

    \item  Liu, S., Ding, Y., Li, J., & Tang, Y. (2021). A Novel End-to-End Sign Language
Recognition System Based on Depth Image Sequences. IEEE Access, 9, 19235-19244.

    \item  Wang, S., Wei, Z., Wang, X., & Gao, W. (2020). Sign Language Recognition via
Attention-Based Temporal Convolutional Network. IEEE Transactions on Multimedia,
22(12), 3192-3203.

    \item  Tan, X., Li, S., & Wang, J. (2021). Sign Language Recognition Using Attention-Based
Deep Neural Networks. IEEE Access, 9, 55518-55527.


    \item  Feng, Z., Zhang, Z., & Wu, Y. (2020). Sign Language Recognition Based on 3D
Convolutional Neural Networks. IEEE Access, 8, 105759-105770.

    \item  Deng, W., Wu, W., & Hu, Z. (2021). Real-Time Sign Language Recognition Based on
MobileNetV2 and ConvLSTM. IEEE Access, 9, 64790-64802.


    \item  Liu, L., Zhang, Y., & Zhang, S. (2020). Sign Language Recognition with Multi-View
Graph Convolutional Networks. IEEE Transactions on Image Processing, 29, 6449-
6461.

    \item  Kim, S., Oh, S., & Kim, Y. (2021). Real-Time Korean Sign Language Recognition
Using Deep Convolutional Neural Networks. Sensors, 21(7), 2552.
\end{enumerate}

