\chapter{Software and Hardware Requirements}
\section{Software Requirements}

\begin{itemize}
    \item Operating System:
   - Windows 10/11, macOS, or Linux (Ubuntu preferred).

    \item Programming Languages:
   - Python (for model development and interface design).

    \item  Development Environment:
   - Integrated Development Environment (IDE) such as PyCharm, Visual Studio Code, or Jupyter Notebook.

    \item Programming Languages:
   - Python (for model development and interface design).

    \item Libraries and Frameworks:
    \begin{itemize}
        \item TensorFlow or PyTorch (for building and training the LSTM model).
        \item OpenCV (for video capture and preprocessing).
        \item NumPy and Pandas (for data manipulation and analysis).
        \item Keras (if using TensorFlow for easier model building).
        \item Scikit-learn (for additional machine learning utilities and metrics).
    \end{itemize}


  \item Data Annotation Tools:
   - LabelImg or VGG Image Annotator (VIA) for annotating sign language data.


 


\end{itemize}
\newpage
\section{ Hardware Requirements}


\begin{itemize}
    \item Processor:
   - Multi-core processor (Intel i5/i7 or AMD Ryzen 5/7 or higher).

    \item RAM:
   - Minimum 16 GB (32 GB recommended for handling large datasets and training models).


    \item  Graphics Processing Unit (GPU):
   - NVIDIA GPU with CUDA support (e.g., NVIDIA GeForce RTX 2070 or higher) for accelerated model training and inference.



  \item Camera:
   - High-definition webcam (for capturing sign language gestures in real-time).




\end{itemize}
